\newpage
\section{Product Requirements}

\subsection{Hardware}
The on purpose build, custom hardware contains all necessary components integrated on a single printed circuit board (PCB). The hardware needs to comply with the following requirements: 
\begin{itemize}
		\item The hardware shall be based around an ESP32 System on Chip.
		\item The hardware shall use LAN/WLAN to communicate with the network router.
		\item The hardware shall have a CAN interface to receive FMS-packages from the vehicle.
		\item The CAN interface shall be galvanically isolated from the rest of the hardware.
		\item The hardware shall have an inertial measurement unit (IMU) with at least 6 axis of freedom.
		\item The hardware shall be able to show the current device status (e.g. LEDs).
		\item The hardware shall be capable of operating with 12 to 24 Volts.
		\item The hardware shall be enclosed in a case in order to minimize dust and moisture getting into the system.
		\item The hardware should have an USB interface for configuration.
\end{itemize}

\subsection{Firmware}
For all use cases defined in \cref{sec:use_cases}, 

\subsection{Web Server Communication Tool}
The web server communication tool is the sole device communicating with the hardware. The system has the following requirements:
\begin{itemize}
        \item The web server shall be written in Python.
        \item The system shall handle http request to achieve a good communication between the embedded system and the host.
        \item The system shall store the streamed data and make it available for further processing.
        \item The system should host files for the hardware (e.g. configuration files, firmware updates).
\end{itemize}

\subsection{Data Interpreter and Visualizer}
This Python-based tool consists of two separated parts and follows the subsequent requirements:

\begin{itemize}
		\item The Data Interpreter shall parse FMS-Packages and prepares them for further usage.
		\item The Data Visualizer shall use a Graphical User Interface (GUI) in order to present the FMS data (e.g. parameter values).
\end{itemize}